Setup

### 2025-04-12 setup.qmd
new plot

This works takes NM CTFM profiles, resamples them and calculates number of
flight present per hour, `H`, of date, `D` in H3 hexagonal cells
(at resolution `R`) covering the EUROCONTROL Member's airspace.

>>>>

This work takes NM CTFM profiles, resamples them and calculates the number of
flight present per hour, `H`, of date, `D` in H3 hexagonal cells
(at resolution `R`) covering the EUROCONTROL Member's airspace.
